An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-07-09 gas-adsorption/rsc-gas-ads-complete.tex
fix typo

\subsection{The real-substrate analog of $\V$ is $\gst$}
\label{sec:phi-is-delta-g}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{g_st_simple.pdf}
    \caption{A illustrative thought experiment to measure $\gst$ by adjusting the altitute difference between two connected volumes, one free space and another containing a porous material.
    $\gst$ is the difference in the gravitational potential energy when the density of gas in each volume is equal.
    % For a given adsorbent and gas, $\gst$=$\gst (\rho, T)$ is defined as the difference in chemical potential between the adsorbed gas system and bulk gas system when both exhibit the same density $\rho$ and temperature $T$. 
    }
    \label{fig:delta-G-cartoon}
\end{figure}

>>>>

\subsection{The real-substrate analog of $\V$ is $\gst$}
\label{sec:phi-is-delta-g}
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{g_st_simple.pdf}
    \caption{An illustrative thought experiment to measure $\gst$ by adjusting the altitute difference between two connected volumes, one free space and another containing a porous material.
    $\gst$ is the difference in the gravitational potential energy when the density of gas in each volume is equal.
    % For a given adsorbent and gas, $\gst$=$\gst (\rho, T)$ is defined as the difference in chemical potential between the adsorbed gas system and bulk gas system when both exhibit the same density $\rho$ and temperature $T$. 
    }
    \label{fig:delta-G-cartoon}
\end{figure}
